Variation in Economic Growth From Civil Conflict

### 2015-04-17 LaTeX/Presentation/PreezeText.tex
preeze updates

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{block}{Puzzle}
High variation in economic performance between countries in the midst of internal armed conflict
\begin{itemize}
\item Mexico
\item India
\item Nicaragua
\end{itemize}
\end{block}

@@

\begin{itemize}
	\item Civil War $\rightarrow$ Economic Performance
	\begin{itemize}
	\item Collier (1999) - \emph{destruction, disruption, diversion, dissaving, portfolio substitution}
	\item Kang \& Meernik (2005) - seek to explain rapid or stagnant post-war recovery
	\end{itemize}
	\item Economic Performance $\rightarrow$ Civil War
	\begin{itemize}
	\item Collier et al. (2003) - the conflict trap
	\item Miguel et al (2004) - rainfall IV for economic shocks
	\end{itemize}
	\item Disaggregating Civil Wars
	\begin{itemize}
	\item Pierskalla \& Hollenbach (2013) - cell phone coverage $\rightarrow$ rebel mobilization
	\end{itemize}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Disaggregating Conflict and Growth}

\begin{block}{Our argument}
State economic performance in countries experiencing civil conflict is conditional on the proximity of conflict from major population, economic, and resource centers
\end{block}

@@

\begin{frame}
\frametitle{FARC guerillas \& the Colombian government}

@@

\end{frame}

@@

\vspace{-0.25cm}
\begin{figure}[ht]
  \centering
  \includegraphics[width=1\textwidth]{CityConfMap-crop}
\end{figure}

@@

\begin{frame}
\frametitle{Aggregating to Country-Year}

\begin{figure}[ht]
	\centering
	\includegraphics[width=.6\textwidth]{colombiaMap-crop}
\end{figure}

\end{frame}

@@

\begin{align*}
	\% \Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{i,t}) \\
	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \;+\; \beta_{5}(Conflict \; Type_{i,t}) \\
	& \;+\; \beta_{6}(Conflict \; Duration_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
	& \;+\; \beta_{8}(Ln(Land \; Area)_{i,t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
\end{align*}

@@

\begin{figure}[ht]
	\centering
	\resizebox{.8\textwidth}{!}{\input{mod3CoefPlot.tex}}
\end{figure}

@@

\begin{frame}
\frametitle{Substantive Effects}

\begin{figure}[ht]
	\centering
	\resizebox{.9\textwidth}{!}{\input{mod3SimPlot.tex}}
\end{figure}

\end{frame}

@@

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}
% \titlepage
% \end{frame}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

High variation in economic performance between countries in the midst of internal armed conflict

\begin{itemize}
\item Mexico
\item India
\item Nicaragua
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Melding of Literatures}

\begin{itemize}
\item Krugman 1991; Henderson 2000; Hanson 2005 - Cities are important drivers of economic growth
\item Heterogeneity in effect of conflict on growth is due to spatial proximity of conflict relative to major urban centers
\end{itemize}

@@

\begin{itemize}
	\item Civil War $\rightarrow$ Economic Performance
	\begin{itemize}
	\item Collier (1999) - destruction, disruption, diversion, dissaving, portfolio substitution
	\item Imai \& Weinstein (2005) - geographical spread of conflict
	\end{itemize}
	\item Economic Performance $\rightarrow$ Civil War
	\begin{itemize}
	\item Collier et al. (2003) - the conflict trap
	\item Fearon \& Laitin (2003) - poor economic growth conducive for civil war
	\end{itemize}
	\item Disaggregating Civil Wars
	\begin{itemize}
	\item Pierskalla \& Hollenbach (2013) - cell phone coverage $\rightarrow$ rebel mobilization
	\end{itemize}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Cities, Conflict, \& Growth}

\begin{itemize}
	\item Cities $\rightarrow$ Growth
	\begin{itemize}
	\item Marshall (1920) - geographic clustering promotes valuable learning and exchange between actors
	\item Lucas (1998) \& Glaeser et al. (1992) - accumulation of human capital generates positive spillovers
	\item Venables (2005) - economy consists of ``lumps'' of productivity and swaths of areas contributing little to growth	
	\end{itemize}
	\item Cities \& Conflict $\rightarrow$ Growth
	\begin{itemize}
	\item Conflicts have heterogeneous effects on economic growth 
	\item Effects determined by spatial proximity to economically relevant centers such as cities
	\end{itemize}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{FARC guerillas \& the Colombian government}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Spread of Conflict: Colombia}

\vspace{-8mm}
\begin{figure}[ht]
	\centering
	\includegraphics[width=.5\textwidth]{colombiaMap-crop}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Spread of Conflict: India}

\vspace{-8mm}
\begin{figure}[ht]
	\centering
	\includegraphics[width=.5\textwidth]{indiaMap-crop}
\end{figure}

@@

% \vspace{-0.25cm}
\begin{figure}[ht]
  \centering
  % \hspace{-50mm}
  \includegraphics[width=1\textwidth]{CityConfMap-crop}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Bivariate Relationship?}

\vspace{-0.25cm}
\begin{figure}[ht]
  \centering
  \resizebox{1\textwidth}{!}{\input{distGdp.tex}}
\end{figure}

@@

\begin{align*}
	\% \Delta Ln(GDP)_{i,t} &= \beta_{1}(Ln(Min. \; Conflict \; Dist.)_{i,t-1}) \\
	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t-1}) \\
	& \;+\; \beta_{3}(Conflict \; Duration_{i,t-1}) \\
	& \;+\; \beta_{4}(Conflict \; Area_{i,t-1} \;/\; Land \; Area_{i,t-1} > 50\%) \\
	& \;+\; \beta_{5}(Number \; of \; Conflicts_{i,t-1}) \\
	& \;+\; \beta_{6}(Upper \; Income_{i,t}) \\	
	& \;+\; \beta_{7}(Inflation_{i,t-1}) \;+\; \beta_{8}(Democracy_{i,t-1}) \\
	& \;+\; \beta_{9}(Resource \; Rents/GDP_{t-1}) \\ 
	& \;+\; \beta_{10}(World \; GDP \; Growth_{t}) \;+\; \mu_{i,t} \;+\; \epsilon_{i,t}
\end{align*}

@@

\vspace{-8mm}
\begin{figure}
	\centering
	\begin{tabular}{cc}
	\hspace{-9mm}
		\resizebox{.5\textwidth}{!}{\input{mCapCoefPlot.tex}} &
		\resizebox{.5\textwidth}{!}{\input{mCityCoefPlot.tex}}
	\end{tabular}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Cross-Validation of Parameter Estimates}

\begin{figure}[ht]
	\centering
	\resizebox{1\textwidth}{!}{\input{crossValPlot.tex}}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Substantive Effects: Capital Distance}

\vspace{-6mm}
\begin{figure}
	\centering
	\resizebox{1\textwidth}{!}{\input{mCapSimPlot.tex}}
\end{figure}

@@
